Process Genotypes For Ancestry Analysis

### 2019-09-20 code/Ancestry_PCA.Rmd
Update Ancestry

## Pull 1000Genomes down and process
* Pull out reference populations (CEU, YRI, CHB, JPT)
```{bash pull_1000Genomes, echo=FALSE}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`

@@

    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz --snps-only --extract LDREF_SNPs.txt --keep 1000G_IDV.list --silent --threads $CORES --make-bed --out 1000Genomes_chr$i
  rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
done
```

```{bash FOO}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`

@@

>>>>

## Pull 1000Genomes down and process
* Pull out reference populations (CEU, YRI, CHB, JPT)
```{bash pull_1000Genomes, echo=FALSE}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
#PATH=$PATH:TWAS/bin/
CORES=`expr $(nproc) - 2`

@@

    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz --snps-only --extract LDREF_SNPs.txt --keep 1000G_IDV.list --silent --threads $CORES --make-bed --out 1000Genomes_chr$i
  rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
done
```
```{bash FOO}
source ~/.bashrc
PATH=$PATH:/home/jgockley/TWAS/bin/
CORES=`expr $(nproc) - 2`

@@

##Plot PCA
```{r PlotPCA}

## Cluster Based on Ancestry
```{bash CLustPrep}
plink --bfile Final_Merge --threads 32 --geno 0.0000001 --recode12 --compound-genotypes --out AllSnps4GemClust
#777864

#Remove non-snp data in the ped file
awk '{$1=$2=$3=$4=$5=$6=""; print $0}' AllSnps4GemClust.ped > foo.txt
perl -pe 's/([^\s]+)\s+([^\s]+)/$1$2/g' foo.txt > poo.txt
awk '{ print $1"_"$2 }' AllSnps4GemClust.ped > foo.txt
paste foo.txt poo.txt > AllGenos4GemClust.txt

cp poo.txt test.txt
sed -i 's/22/2/g' test.txt
sed -i 's/00/3/g' test.txt
sed -i 's/12/1/g' test.txt
sed -i 's/11/0/g' test.txt

paste foo.txt test.txt > AllGenos4GemClust.txt
sed -i 's/\t/ /g' AllGenos4GemClust.txt
sed -i 's/  */ /g' AllGenos4GemClust.txt
